ext_risk_copula

### 2019-01-27 ext_risk_copula.Rmd
try to add austin-brewer model

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Pennycuick model : a = 1, b = 3) with global dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_global_disp_msmith_r_vary}](./Results/pennycuick/pennycuick_ext_risk_global_disp.pdf){ width=40%, height=40% }

>>>>

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Pennycuick model : a = 0.1, b = 0.1) with global dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_global_disp_msmith_r_vary}](./Results/pennycuick/pennycuick_ext_risk_global_disp.pdf){ width=40%, height=40% }
